---
title: "Pilot Study Write-Up"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r packages}
library(tidyverse)
library(stringr)
library(readr)

```


# Overview

This is a file to provide descriptive information for use in the registered report being prepared by the Piloting taskforce fixme.  The text is a starting point and is edited in the main file. 
---

```{r read-coding-files}
# read manual coding files
manual1 = read.csv("data/2025-12-09_Codingform_PilotingAssessment_pilot.csv")
manual1$coding = "pilot1"
manual2 = read.csv("data/2026-04-03_Codingform_PilotingAssessment_pilot2.csv")
manual2$coding = "pilot2"
# combine both pilots
manual = bind_rows(manual1, manual2)

# make clean doi column, remove .org inclusion
manual <- manual %>%
  mutate(
    doi = X1.2..Article.DOI |>
      sub("^https?://doi\\.org/", "", x = _) |>
      sub("^doi\\.org/", "", x = _) |>
      sub("(?i)^doi:\\s*", "", x = _, perl = TRUE) |>
      str_trim()
  )

# data for manual analysis
data = 
  manual %>%
  # remove "test" data
  filter(doi != "test") %>%
  # add rough indicator of whether pilot study was conducted
  mutate(includes_pilot = ifelse(str_detect(X1.3..Is.there.a.statement.in.the.article.that.there.was.a.pilot.study.conducted., "Yes"), "yes", "other"))


dois = 
  data %>%
  distinct(doi) %>%
  pull(doi)
```

```{r extract-data-auto, eval=FALSE}
# extract automated coding
# only run if you want to be able to run the automated extraction code below, otherwise you can just load the data from the .csv files (done below)
source("extract_doi_metadata.R")

auto_databases <- process_dois(dois, return_location_details = TRUE)

# add meta check-inspired coding using TEIs
# created using extract_tei_coi_funding.R
# fixme add through csv for now, needs TEIs
# only done for pilot2
auto_tei = read.csv("data/tei_coi_funding_extracted.csv")

# combine files 
comb = 
  manual %>%
  full_join(
    auto_databases, 
    by = "doi"
    ) %>%
  full_join(
    auto_tei,
    by = "doi"
  )

# Drop any AsIs list-columns before saving — they serialize as unquoted R list()
# notation in CSV, corrupting all downstream columns
comb |>
  select(where(~ !inherits(.x, "AsIs") && !is.list(.x))) |>
  write.csv("data/2026-06-11_auto-and-manual-combined_pilot1-and-pilot2.csv", row.names = FALSE)

```

```{r load-combined-data-auto-extracted}
# load combined data
comb = read_csv("data/2026-06-11_auto-and-manual-combined_pilot1-and-pilot2.csv")


```

```{r}
# add information to combined file about extracted info on funding and coi
comb = 
  comb %>%
  # remove "test" data
  filter(doi != "test") %>%
  # add rough indicator of whether pilot study was conducted
  mutate(includes_pilot = ifelse(str_detect(X1.3..Is.there.a.statement.in.the.article.that.there.was.a.pilot.study.conducted., "Yes"), "yes", "other")) %>%
  # indicator of whether funding info was extracted
  mutate(
    funding_auto_extracted = if_any(starts_with("funding"), ~ 
                              !is.na(.) & str_trim(.) != "" & !str_to_lower(.) %in% c("na", "n/a")
    ),
    funding_manual_extracted = !is.na(.data[["X8.1..Does.the.article.include.a.funding.statement."]]) &
      str_trim(.data[["X8.1..Does.the.article.include.a.funding.statement."]]) != "" &
      !str_to_lower(.data[["X8.1..Does.the.article.include.a.funding.statement."]]) %in% c("na", "n/a")
  ) %>%
  # indicator of whether COI info was extracted
  mutate(
    coi_auto_extracted = if_any(starts_with("coi"), ~ 
                              !is.na(.) & str_trim(.) != "" & !str_to_lower(.) %in% c("na", "n/a")|
                              if_any(starts_with("rx_coi"), ~ !is.na(.))
    ),
    coi_manual_extracted_content_available = !is.na(.data[["X8.2.1..If.there.is.a.conflict.of.interest.statement..what.is.the.statement."]]) &
      str_trim(.data[["X8.2.1..If.there.is.a.conflict.of.interest.statement..what.is.the.statement."]]) != "" &
      !str_to_lower(.data[["X8.2.1..If.there.is.a.conflict.of.interest.statement..what.is.the.statement."]]) %in% c("na", "n/a")
  ) %>%
  mutate(manual_does_include_coi = 
           ifelse(coding == "pilot1", 
                  X8.2..Does.the.article.include.a.statement.indicating.whether.there.were.any.conflicts.of.interest.,
                  X8.2..Does.the.article.include.a.statement.indicating.whether.there.were.any.conflicts.of.interest..COI..)) 

```
# Pilot study 1

## Pilot sample

```{r pilot1-sample}
pilot1_sample_papers = 
  data %>%
  filter(coding == "pilot1") %>%
  distinct(doi, .keep_all = TRUE) %>%
  group_by(includes_pilot) %>%
  summarise(n_papers = n())

pilot1_sample_coders = 
  data %>%
  filter(coding == "pilot1") %>%
  distinct(doi, X1.1..Coder.Initials) %>%
  group_by(X1.1..Coder.Initials) %>%
  summarise(n_papers = n()) 

```

`r sum(pilot1_sample_papers$n_papers)` papers were inspected by `r nrow(pilot1_sample_coders)` coders in the first pilot study. Out of these `r sum(pilot1_sample_papers$n_papers)` papers, `r pilot1_sample_papers$n_papers[pilot1_sample_papers$includes_pilot == "yes"]` (`r round(pilot1_sample_papers$n_papers[pilot1_sample_papers$includes_pilot == "yes"] / sum(pilot1_sample_papers$n_papers) * 100, 1)`%) papers included a statement that a pilot study was conducted, while `r pilot1_sample_papers$n_papers[pilot1_sample_papers$includes_pilot != "yes"]` (`r round(pilot1_sample_papers$n_papers[pilot1_sample_papers$includes_pilot != "yes"] / sum(pilot1_sample_papers$n_papers) * 100, 1)`%) papers did not include such a statement.

## Pilot data extraction

### Manual

### Automatic


```{r}
auto_pilot1 = 
  comb %>%
  filter(coding == "pilot1") %>%
  select(where(~ !all(is.na(.))))  %>%
  # remove "test" data
  filter(doi != "test") %>%
  filter(includes_pilot == "yes")
```



```{r auto-pilot1-extraction-completeness}
auto1_n <- nrow(auto_pilot1)

# Basic publication metadata (OpenAlex)
auto1_n_year    <- sum(!is.na(auto_pilot1$year))
auto1_n_journal <- sum(!is.na(auto_pilot1$journal))
auto1_n_issn    <- sum(!is.na(auto_pilot1$issn))

# Author affiliation and location (OpenAlex)
auto1_n_first_loc <- sum(
  !is.na(auto_pilot1$first_author_location) &
    str_trim(auto_pilot1$first_author_location) != ""
)
auto1_n_last_loc <- sum(
  !is.na(auto_pilot1$last_author_location) &
    str_trim(auto_pilot1$last_author_location) != ""
)
auto1_n_first_country <- sum(!is.na(auto_pilot1$first_author_location_detail_country))
auto1_n_last_country  <- sum(!is.na(auto_pilot1$last_author_location_detail_country))

# Primary topic classification (OpenAlex)
auto1_n_topic <- sum(
  !is.na(auto_pilot1$primary_topic_display_name) &
    str_trim(auto_pilot1$primary_topic_display_name) != ""
)

# Funding (Crossref)
auto1_n_funding <- sum(
  (!is.na(auto_pilot1$funding_funders_crossref)    & str_trim(auto_pilot1$funding_funders_crossref)    != "") |
  (!is.na(auto_pilot1$funding_funder_ids_crossref) & str_trim(auto_pilot1$funding_funder_ids_crossref) != "") |
  (!is.na(auto_pilot1$funding_award_ids_crossref)  & str_trim(auto_pilot1$funding_award_ids_crossref)  != ""),
  na.rm = TRUE
)

# Conflict of interest statements (Crossref)
auto1_n_coi <- sum(
  !is.na(auto_pilot1$coi_crossref) &
    str_trim(auto_pilot1$coi_crossref) != "" &
    !str_to_lower(auto_pilot1$coi_crossref) %in% c("na", "n/a"),
  na.rm = TRUE
)

# Abstracts (Crossref)
auto1_n_abstract <- sum(
  !is.na(auto_pilot1$cr_abstract) &
    str_trim(auto_pilot1$cr_abstract) != ""
)

# Helper: format as "n (x%)"
auto1_pct <- function(n) round(n / auto1_n * 100, 1)
```

We automatically extracted information for the  `r auto1_n` DOIs for which manual coders indicated that a pilot was reported in the manuscript. 

This first round of automatic data extraction was conducted using API-based queries to OpenAlex and Crossref. OpenAlex was used to extract basic publication metadata — year, journal name, and ISSN were available for all papers. 
<!--`r auto1_n_year` papers (`r auto1_pct(auto1_n_year)`%), `r auto1_n_journal` papers (`r auto1_pct(auto1_n_journal)`%), and `r auto1_n_issn` papers (`r auto1_pct(auto1_n_issn)`%), respectively. -->
Author affiliation and location information for the first and last authors was extracted from both article-level authorship records and author profile lookups (including institution name, country, city, and geographic coordinates). Both first and last author location information were available for all papers. 
<!-- first author location was available for `r auto1_n_first_loc` papers (`r auto1_pct(auto1_n_first_loc)`%) and last author location for `r auto1_n_last_loc` papers (`r auto1_pct(auto1_n_last_loc)`%). Country-level information specifically was available for `r auto1_n_first_country` (`r auto1_pct(auto1_n_first_country)`%) and `r auto1_n_last_country` (`r auto1_pct(auto1_n_last_country)`%) papers for first and last authors, respectively.--> 
Primary topic classification was furthermore available for `r auto1_n_topic` papers (`r auto1_pct(auto1_n_topic)`%). 

Crossref was used to extract funding information (funder names, funder IDs, and award IDs; available for `r auto1_n_funding` papers, `r auto1_pct(auto1_n_funding)`%), conflict of interest (COI) statements (available for `r auto1_n_coi` papers, `r auto1_pct(auto1_n_coi)`%), and abstracts (available for `r auto1_n_abstract` papers, `r auto1_pct(auto1_n_abstract)`%).

```{r auto-pilot1-funding-coi-overlap}
# Funding: overlap between auto and manual extraction
fund_tbl <- auto_pilot1 |>
  count(funding_auto_extracted, funding_manual_extracted)

auto1_fund_auto_and_manual <- fund_tbl |> filter(funding_auto_extracted,  funding_manual_extracted) |> pull(n)
auto1_fund_auto_only       <- fund_tbl |> filter(funding_auto_extracted, !funding_manual_extracted) |> pull(n)
auto1_fund_manual_only     <- fund_tbl |> filter(!funding_auto_extracted, funding_manual_extracted) |> pull(n)
auto1_fund_neither         <- fund_tbl |> filter(!funding_auto_extracted,!funding_manual_extracted) |> pull(n)

auto1_fund_auto_total      <- auto1_fund_auto_and_manual + auto1_fund_auto_only
auto1_fund_not_auto_total  <- auto1_fund_manual_only + auto1_fund_neither
auto1_fund_pct_also_manual <- round(auto1_fund_auto_and_manual / auto1_fund_auto_total * 100, 1)
auto1_fund_pct_substitute  <- round(auto1_fund_manual_only / auto1_fund_not_auto_total * 100, 1)

# COI: overlap between auto and manual extraction
# any "Yes" manual answer = manual COI statement available
coi_tbl <- auto_pilot1 |>
  mutate(coi_manual_has_stmt = str_starts(manual_does_include_coi, "Yes")) |>
  count(coi_auto_extracted, coi_manual_has_stmt)

auto1_coi_auto_and_manual <- coi_tbl |> filter(coi_auto_extracted,  coi_manual_has_stmt) |> pull(n) |> sum()
auto1_coi_auto_only       <- coi_tbl |> filter(coi_auto_extracted, !coi_manual_has_stmt) |> pull(n) |> sum()
auto1_coi_manual_only     <- coi_tbl |> filter(!coi_auto_extracted, coi_manual_has_stmt) |> pull(n) |> sum()
auto1_coi_neither         <- coi_tbl |> filter(!coi_auto_extracted,!coi_manual_has_stmt) |> pull(n) |> sum()

auto1_coi_auto_total      <- auto1_coi_auto_and_manual + auto1_coi_auto_only
auto1_coi_not_auto_total  <- auto1_coi_manual_only + auto1_coi_neither
auto1_coi_pct_also_manual <- round(auto1_coi_auto_and_manual / auto1_coi_auto_total * 100, 1)
auto1_coi_pct_substitute  <- round(auto1_coi_manual_only / auto1_coi_not_auto_total * 100, 1)

# Manual-perspective totals (for prose starting from "manually extracted for X papers")
auto1_fund_manual_total       <- auto1_fund_auto_and_manual + auto1_fund_manual_only
auto1_fund_pct_auto_of_manual <- round(auto1_fund_auto_and_manual / auto1_fund_manual_total * 100, 1)
auto1_fund_no_manual_total    <- auto1_fund_auto_only + auto1_fund_neither
auto1_fund_pct_sub_no_manual  <- round(auto1_fund_auto_only / auto1_fund_no_manual_total * 100, 1)

auto1_coi_manual_total        <- auto1_coi_auto_and_manual + auto1_coi_manual_only
auto1_coi_pct_auto_of_manual  <- round(auto1_coi_auto_and_manual / auto1_coi_manual_total * 100, 1)
auto1_coi_no_manual_total     <- auto1_coi_auto_only + auto1_coi_neither
auto1_coi_pct_sub_no_manual   <- round(auto1_coi_auto_only / auto1_coi_no_manual_total * 100, 1)
```

We compared the quantity of automated and manually extracted funding and COI statements to get an idea of the possibility of replacing the manual coding with the automated approach.
Funding information was manually extracted for `r auto1_fund_manual_total` papers, of which `r auto1_fund_auto_and_manual` papers also had this information automatically extracted (`r auto1_fund_pct_auto_of_manual`%). For the `r auto1_fund_no_manual_total` papers for which manual funding information was absent, `r auto1_fund_auto_only` papers could be supplemented with automated extraction (`r auto1_fund_pct_sub_no_manual`%). For COI statements, manual coders recorded a COI statement for `r auto1_coi_manual_total` papers, of which `r auto1_coi_auto_and_manual` papers also had a COI statement automatically extracted (`r auto1_coi_pct_auto_of_manual`%). For the `r auto1_coi_no_manual_total` papers without a manually coded COI statement, `r auto1_coi_auto_only` papers had a COI statement available from automated extraction (`r auto1_coi_pct_sub_no_manual`%).

<!-- For the funding information, of the `r auto1_fund_auto_total` papers where it was automatically extracted, it was also manually coded for `r auto1_fund_auto_and_manual` papers (`r auto1_fund_pct_also_manual`%). For the `r auto1_fund_not_auto_total` papers where funding information was absent from the automated extraction, manual coding could supplement this for `r auto1_fund_manual_only` papers (`r auto1_fund_pct_substitute`%). For COI statements, all `r auto1_coi_auto_and_manual` papers where a COI statement was automatically extracted also had a COI statement recorded by manual coders (`r auto1_coi_pct_also_manual`%). Of the `r auto1_coi_not_auto_total` papers where automated extraction did not yield a COI statement, manual coders recorded a COI statement for `r auto1_coi_manual_only` papers (`r auto1_coi_pct_substitute`%). -->

Qualitative inspection of the automated extraction showed that the metadata extracted from OpenAlex for the primary topic classification did not match the topics sufficiently.



See section fixme below for details. 

## Results
Based on the first pilot study, we adjusted the coding form to include FIXME. 

--- 

# Pilot study 2

## Pilot sample

```{r pilot2-sample}
pilot2_sample_papers = 
  data %>%
  filter(coding == "pilot2") %>%
  distinct(doi, .keep_all = TRUE) %>%
  group_by(includes_pilot) %>%
  summarise(n_papers = n())

pilot2_sample_coders = 
  data %>%
  filter(coding == "pilot2") %>%
  distinct(doi, X1.1..Coder.Initials) %>%
  group_by(X1.1..Coder.Initials) %>%
  summarise(n_papers = n()) 

```

`r sum(pilot2_sample_papers$n_papers)` papers were inspected by `r nrow(pilot2_sample_coders)` coders in the second pilot study. Out of these `r sum(pilot2_sample_papers$n_papers)` papers, `r pilot2_sample_papers$n_papers[pilot2_sample_papers$includes_pilot == "yes"]` (`r round(pilot2_sample_papers$n_papers[pilot2_sample_papers$includes_pilot == "yes"] / sum(pilot2_sample_papers$n_papers) * 100, 1)`%) papers included a statement that a pilot study was conducted, while `r pilot2_sample_papers$n_papers[pilot2_sample_papers$includes_pilot != "yes"]` (`r round(pilot2_sample_papers$n_papers[pilot2_sample_papers$includes_pilot != "yes"] / sum(pilot2_sample_papers$n_papers) * 100, 1)`%) papers did not include such a statement.

## Pilot data extraction

### Manual

### Automatic

```{r}
auto_pilot2 = 
  comb %>%
  filter(coding == "pilot2") %>%
  select(where(~ !all(is.na(.))))  %>%
  # remove "test" data
  filter(doi != "test") %>%
  filter(includes_pilot == "yes")
```


```{r auto-pilot2-extraction-completeness}
auto2_n <- nrow(auto_pilot2)

# Basic publication metadata (OpenAlex)
auto2_n_year    <- sum(!is.na(auto_pilot2$year))
auto2_n_journal <- sum(!is.na(auto_pilot2$journal))
auto2_n_issn    <- sum(!is.na(auto_pilot2$issn))

# Author affiliation and location (OpenAlex)
auto2_n_first_loc <- sum(
  !is.na(auto_pilot2$first_author_location) &
    str_trim(auto_pilot2$first_author_location) != ""
)
auto2_n_last_loc <- sum(
  !is.na(auto_pilot2$last_author_location) &
    str_trim(auto_pilot2$last_author_location) != ""
)
auto2_n_first_country <- sum(!is.na(auto_pilot2$first_author_location_detail_country))
auto2_n_last_country  <- sum(!is.na(auto_pilot2$last_author_location_detail_country))

# Primary topic classification (OpenAlex)
auto2_n_topic <- sum(
  !is.na(auto_pilot2$primary_topic_display_name) &
    str_trim(auto_pilot2$primary_topic_display_name) != ""
)

# Funding (Crossref)
auto2_n_funding <- sum(
  (!is.na(auto_pilot2$funding_funders_crossref)    & str_trim(auto_pilot2$funding_funders_crossref)    != "") |
  (!is.na(auto_pilot2$funding_funder_ids_crossref) & str_trim(auto_pilot2$funding_funder_ids_crossref) != "") |
  (!is.na(auto_pilot2$funding_award_ids_crossref)  & str_trim(auto_pilot2$funding_award_ids_crossref)  != ""),
  na.rm = TRUE
)

# Conflict of interest statements (Crossref)
auto2_n_coi <- sum(
  !is.na(auto_pilot2$coi_crossref) &
    str_trim(auto_pilot2$coi_crossref) != "" &
    !str_to_lower(auto_pilot2$coi_crossref) %in% c("na", "n/a"),
  na.rm = TRUE
)

# Abstracts (Crossref)
auto2_n_abstract <- sum(
  !is.na(auto_pilot2$cr_abstract) &
    str_trim(auto_pilot2$cr_abstract) != ""
)

# Helper: format as "n (x%)"
auto2_pct <- function(n) round(n / auto2_n * 100, 1)
```

We automatically extracted information for the  `r auto2_n` DOIs for which manual coders indicated that a pilot was reported in the manuscript. 

We again employed OpenAlex and Crossref to extract metadata. Year, journal name, and ISSN were available for all papers through OpenAlex. 
<!--`r auto2_n_year` papers (`r auto2_pct(auto2_n_year)`%), `r auto2_n_journal` papers (`r auto2_pct(auto2_n_journal)`%), and `r auto2_n_issn` papers (`r auto2_pct(auto2_n_issn)`%), respectively. -->
First author country location was available for `r auto2_n_first_loc` papers (`r auto2_pct(auto2_n_first_loc)`%) and last author location for all `r auto2_n_last_loc` papers (`r auto2_pct(auto2_n_last_loc)`%). <!-- Country-level information specifically was available for `r auto2_n_first_country` (`r auto2_pct(auto2_n_first_country)`%) and `r auto2_n_last_country` (`r auto2_pct(auto2_n_last_country)`%) papers for first and last authors, respectively.-->
<!-- Primary topic classification was again available for `r auto2_n_topic` papers (`r auto2_pct(auto2_n_topic)`%). -->

Crossref was used to extract funding information (funder names, funder IDs, and award IDs; available for `r auto2_n_funding` papers, `r auto2_pct(auto2_n_funding)`%), conflict of interest (COI) statements (available for `r auto2_n_coi` papers, `r auto2_pct(auto2_n_coi)`%), and abstracts (available for `r auto2_n_abstract` papers, `r auto2_pct(auto2_n_abstract)`%).

```{r auto-pilot2-tei-completeness}
auto2_n_tei         <- sum(!is.na(auto_pilot2$rx_funding_found) | !is.na(auto_pilot2$rx_coi_found))
auto2_n_tei_funding <- sum(auto_pilot2$rx_funding_found, na.rm = TRUE)
auto2_n_tei_coi     <- sum(auto_pilot2$rx_coi_found, na.rm = TRUE)
```

To supplement the API-based extraction described above, we additionally processed the article PDFs to extract funding and COI statements directly from the full text. Article PDFs were converted to structured TEI XML using GROBID, an open-source machine learning library for parsing scientific documents. TEI files were available for `r auto2_n_tei` of the `r auto2_n` papers. 

We applied two complementary extraction approaches to these files. First, we used the `metacheck` R package (FIXME cite), which is designed to parse GROBID-generated TEI files and run structured compliance checks, including binary detection of funding acknowledgements and COI disclosures. Second, we developed a custom XPath- and regex-based extraction pipeline that directly queries the structured back-matter and body sections of the TEI XML, using heading-pattern matching (e.g., matching section headings containing phrases such as "conflict of interest", "funding", "acknowledgements").

```{r}
# fixme add code? now info taken from README_tei_extraction.md
tei_pilot2_funding_accuracy = 0.963
tei_pilot2_coi_accuracy = 0.926

tei_pilot2_funding_precision = 0.957
tei_pilot2_coi_precision = 0.984

tei_pilot2_funding_recall = 1.000
tei_pilot2_coi_recall = 0.924

tei_pilot2_funding_f1 = 0.978
tei_pilot2_coi_f1 = 0.953

# Helper: reconstruct approximate confusion-matrix counts from rounded metrics
metrics_to_counts <- function(n, accuracy, precision, recall) {
  possible <- expand.grid(
    tp = 0:n,
    fp = 0:n,
    fn = 0:n,
    tn = 0:n
  ) |>
    dplyr::filter(tp + fp + fn + tn == n) |>
    dplyr::mutate(
      accuracy_calc  = (tp + tn) / n,
      precision_calc = dplyr::if_else(tp + fp == 0, NA_real_, tp / (tp + fp)),
      recall_calc    = dplyr::if_else(tp + fn == 0, NA_real_, tp / (tp + fn)),
      error = abs(accuracy_calc - accuracy) +
        abs(precision_calc - precision) +
        abs(recall_calc - recall)
    ) |>
    dplyr::arrange(error)

  possible[1, c("tp", "fp", "fn", "tn")]
}

auto2_funding_counts <- metrics_to_counts(
  n = auto2_n_tei,
  accuracy = tei_pilot2_funding_accuracy,
  precision = tei_pilot2_funding_precision,
  recall = tei_pilot2_funding_recall
)

auto2_coi_counts <- metrics_to_counts(
  n = auto2_n_tei,
  accuracy = tei_pilot2_coi_accuracy,
  precision = tei_pilot2_coi_precision,
  recall = tei_pilot2_coi_recall
)

# Funding
auto2_funding_auto_and_manual <- auto2_funding_counts$tp
auto2_funding_auto_only       <- auto2_funding_counts$fp
auto2_funding_manual_only     <- auto2_funding_counts$fn
auto2_funding_neither         <- auto2_funding_counts$tn

auto2_funding_auto_total      <- auto2_funding_auto_and_manual + auto2_funding_auto_only
auto2_funding_not_auto_total  <- auto2_funding_manual_only + auto2_funding_neither

auto2_funding_pct_also_manual <- round(
  auto2_funding_auto_and_manual / auto2_funding_auto_total * 100, 1
)

auto2_funding_pct_substitute <- round(
  auto2_funding_manual_only / auto2_funding_not_auto_total * 100, 1
)

# COI
auto2_coi_auto_and_manual <- auto2_coi_counts$tp
auto2_coi_auto_only       <- auto2_coi_counts$fp
auto2_coi_manual_only     <- auto2_coi_counts$fn
auto2_coi_neither         <- auto2_coi_counts$tn

auto2_coi_auto_total      <- auto2_coi_auto_and_manual + auto2_coi_auto_only
auto2_coi_not_auto_total  <- auto2_coi_manual_only + auto2_coi_neither

auto2_coi_pct_also_manual <- round(
  auto2_coi_auto_and_manual / auto2_coi_auto_total * 100, 1
)

auto2_coi_pct_substitute <- round(
  auto2_coi_manual_only / auto2_coi_not_auto_total * 100, 1
)

# Manual-perspective totals
auto2_funding_manual_total       <- auto2_funding_auto_and_manual + auto2_funding_manual_only
auto2_funding_pct_auto_of_manual <- round(auto2_funding_auto_and_manual / auto2_funding_manual_total * 100, 1)
auto2_funding_no_manual_total    <- auto2_funding_auto_only + auto2_funding_neither
auto2_funding_pct_sub_no_manual  <- round(auto2_funding_auto_only / auto2_funding_no_manual_total * 100, 1)

auto2_coi_manual_total           <- auto2_coi_auto_and_manual + auto2_coi_manual_only
auto2_coi_pct_auto_of_manual     <- round(auto2_coi_auto_and_manual / auto2_coi_manual_total * 100, 1)
auto2_coi_no_manual_total        <- auto2_coi_auto_only + auto2_coi_neither
auto2_coi_pct_sub_no_manual      <- round(auto2_coi_auto_only / auto2_coi_no_manual_total * 100, 1)

```

Based on the custom approach, which outperformed metacheck (version fixme), we were able to match the manual coding for funding and COI statements with high accuracy.

Funding information was manually extracted for `r auto2_funding_manual_total` papers, of which `r auto2_funding_auto_and_manual` papers also had this information automatically extracted (`r auto2_funding_pct_auto_of_manual`%). For the `r auto2_funding_no_manual_total` papers for which manual funding information was absent, `r auto2_funding_auto_only` papers could be supplemented with automated extraction (`r auto2_funding_pct_sub_no_manual`%). For COI statements, manual coders recorded a COI statement for `r auto2_coi_manual_total` papers, of which `r auto2_coi_auto_and_manual` papers also had a COI statement automatically extracted (`r auto2_coi_pct_auto_of_manual`%). For the `r auto2_coi_no_manual_total` papers without a manually coded COI statement, `r auto2_coi_auto_only` papers had a COI statement available from automated extraction (`r auto2_coi_pct_sub_no_manual`%).


Qualitative inspection FIXMe. 

See section fixme below for details. 

# Main study

## Data extraction

### Automated data extraction
```{r select-dois}
# select dois with manual coding
dois = data$doi
## remove "test" entries
dois = dois[dois != "test"]
## keep only unique entries
dois = unique(dois)
```

### Manual data extraction
