---
title: "Pilot Study Write-Up"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r packages}
library(tidyverse)
library(stringr)
```



# Overview

This is a file to provide descriptive information for use in the registered report being prepared by the Piloting taskforce fixme. 
---

```{r read-coding-files}
# read manual coding files
manual1 = read.csv("data/2025-12-09_Codingform_PilotingAssessment_pilot.csv")
manual1$coding = "pilot1"
manual2 = read.csv("data/2026-04-03_Codingform_PilotingAssessment_pilot2.csv")
manual2$coding = "pilot2"
# combine both pilots
manual = bind_rows(manual1, manual2)

# make clean doi column, remove .org inclusion
manual <- manual %>%
  mutate(
    doi = X1.2..Article.DOI |>
      sub("^https?://doi\\.org/", "", x = _) |>
      sub("^doi\\.org/", "", x = _) |>
      sub("(?i)^doi:\\s*", "", x = _, perl = TRUE) |>
      str_trim()
  )

# data for analysis
data = 
  manual %>%
  # remove "test" data
  filter(doi != "test") %>%
  # add rough indicator of whether pilot study was conducted
  mutate(includes_pilot = ifelse(str_detect(X1.3..Is.there.a.statement.in.the.article.that.there.was.a.pilot.study.conducted., "Yes"), "yes", "other"))
```


# Pilot study 1

## Pilot sample


## Pilot data extraction

### Manual
```{r pilot1-sample}
pilot1_sample_papers = 
  data %>%
  filter(coding == "pilot1") %>%
  distinct(doi, .keep_all = TRUE) %>%
  group_by(includes_pilot) %>%
  summarise(n_papers = n())

pilot1_sample_coders = 
  data %>%
  filter(coding == "pilot1") %>%
  distinct(doi, X1.1..Coder.Initials) %>%
  group_by(X1.1..Coder.Initials) %>%
  summarise(n_papers = n()) 

```

`r sum(pilot1_sample_papers$n_papers)` papers were inspected by `r nrow(pilot1_sample_coders)` coders in the first pilot study. Out of these `r sum(pilot1_sample_papers$n_papers)` papers, `r pilot1_sample_papers$n_papers[pilot1_sample_papers$includes_pilot == "yes"]` (`r round(pilot1_sample_papers$n_papers[pilot1_sample_papers$includes_pilot == "yes"] / sum(pilot1_sample_papers$n_papers) * 100, 1)`%) papers included a statement that a pilot study was conducted, while `r pilot1_sample_papers$n_papers[pilot1_sample_papers$includes_pilot != "yes"]` (`r round(pilot1_sample_papers$n_papers[pilot1_sample_papers$includes_pilot != "yes"] / sum(pilot1_sample_papers$n_papers) * 100, 1)`%) papers did not include such a statement.

### Automatic
```{r select-dois}
# select dois with manual coding
dois = data$doi
## remove "test" entries
dois = dois[dois != "test"]
## keep only unique entries
dois = unique(dois)
```


--- 

# Pilot study 2

## Pilot sample

```{r pilot2-sample}
# 
```

## Pilot data extraction

### Manual

### Automatic

# Main study

## Data extraction

### Automated data extraction

### Manual data extraction
